### 2016-12-21 tags/2016-v0.4.12/docs/references.tex
Tag of final v0.4.12
git-svn-id: https://ccpforge.cse.rl.ac.uk/svn/ludwig@3055 40876441-3496-0410-a613-a2fca35b2ae2

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%  references.tex
%
%  Bibliography
%
%  $Id: references.tex 1902 2013-01-31 15:11:10Z ohenrich $
%
%  Edinburgh Soft Matter and Statistical Physics Group and
%  Edinburgh Parallel Computing Centre
%
%  Kevin Stratford (kevin@epcc.ed.ac.uk)
%  (c) 2011 The University of Edinburgh
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\bibitem{adhikari-desplat2005}
Adhikari, R. J.-C. Desplat, and K. Stratford,
Sliding periodic boundary conditions for lattice Boltzmann and lattice
kinetic equations,
\texttt{arXiv:cond-mat/0503175v1} (2005).

@@

\bibitem{allen-tildesley}
M.P. Allen and D.J. Tildesley,
\textit{Computer simulation of liquids},
Oxford University Press (1987).

@@

\bibitem{beris-edwards}
Beris, A.N., and B.J. Edwards,
\textit{Thermodynamics of flowing systems with internal microstructure},
Oxford University Press (1994).

@@

\bibitem{cahn-hilliard-1958}
J.W. Cahn and J.E. Hilliard,
Free energy of a nonuniform system. I. Interfacial free energy,
\textit{J. Chem. Phys.} \textbf{28} 258--267 (1958).

@@

\bibitem{degennes-prost2002}
de Gennes, J.-G., and J. Prost,
\textit{The physics of liquid crystals},
Oxford University Press (2002).

@@

\bibitem{lees-edwards1972}
A.W. Lees and S.F. Edwards,
The computer study of transport processes under extreme conditions,
\textit{J. Phys C} \textbf{5} 1921--1929 (1972).

@@

\bibitem{rapaport1995}
Rapaport, D.C., \textit{The Art of Molecular Dynamics Simulation},
Cambridge University Press, 1995.

\bibitem{j-stat-phys-2005}
K. Stratford, R. Adhikari, I. Pagonabarraga, and J.-C. Desplat,
Lattice Boltzmann for binary fluids with suspended colloids,
\textit{J. Stat. Phys.} \textbf{121} 163--178 (2005).

\bibitem{swift1996}
M.R. Swift, E. Orlandini, W.R. Osborn, and J.M. Yeomans,
Lattice Boltzmann simulations of liquid-gas and binary fluid systems,
\textit{Phys. Rev. E} \textbf{54} 5041--5052 (1996).

@@

@@

\bibitem{wagner-pagonabarraga2002}
A.J. Wagner and I. Pagonabarraga,
Lees-Edwards boundary conditions of lattice Boltzmann,
\textit{J. Stat. Phys.} \textbf{107} 521--537 (2002).

@@

\bibitem{wright-mermin}
Wright, D.C> and N.D. Mermin,
\textit{Rev. Mod. Phys.} \textbf{61}, 385--432 (1989).

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%  references.tex
%
%  Bibliography
%
%  $Id: references.tex 1902 2013-01-31 15:11:10Z ohenrich $
%
%  Edinburgh Soft Matter and Statistical Physics Group and
%  Edinburgh Parallel Computing Centre
%
%  (c) 2011-2016 The University of Edinburgh
%  Kevin Stratford (kevin@epcc.ed.ac.uk)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\bibitem{adhikari_desplat}
Adhikari, R. J.-C. Desplat, and K. Stratford,
Sliding periodic boundary conditions for lattice Boltzmann and lattice
kinetic equations,
\texttt{arXiv:cond-mat/0503175v1} (2005).

@@

@@

@@

\bibitem{cahn-hilliard-1958}
J.W. Cahn and J.E. Hilliard,
Free energy of a nonuniform system. I: Interfacial free energy,
\textit{J. Chem. Phys.}, \textbf{28}, 258--267 (1958).

@@

@@

@@

\bibitem{r95}
Rapaport, D.C., \textit{The Art of Molecular Dynamics Simulation},
Cambridge University Press, 1995.

\bibitem{j-stat-phys-2005}
K. Stratford, R. Adhikari, I. Pagonabarraga, and J.-C. Desplat,
Lattice Boltzmann for binary fluids with suspended colloids,
\textit{J. Stat. Phys.}, \textbf{121}, 163--178 (2005).

@@

\bibitem{swift1996}
M.R. Swift, E. Orlandini, W.R. Osborn, and J.M. Yeomans,
Lattice Boltzmann simulation of liquid-gas and binary fluid systems,
\textit{Phys. Rev. E}, \textbf{54} 5041 (1996).

@@

@@

\bibitem{wright}
D.C. Wright and N.D. Mermin,
\textit{Rev. Mod. Phys.} \textbf{61}, 385 (1989).
